Supplementary Material

### 2019-04-19 Paper/Supplement/Supplement.tex
Names Supplementary Tables

\begin{center}
 \begin{longtable}{|| c | c||} 
 \hline
 Name & Description  \\ [0.5ex] 
 \hline
 $p$ & proliferation rate of tissue cells \\ 
 \hline
 $d_C$  & death rate of tissue cells \\
 \hline
$\Delta_\text{MIE}$ &  mesenchymal immune evasion \\
 \hline
 $\Delta_\text{MGA}$ & mesenchymal growth arrest    \\
 \hline
  $\Delta_A$ & mutant cells decreased apoptosis  \\
  \hline
  $\Delta_\text{IE}$ & mutant cells increased immune evasion  \\
  \hline
  $\Delta_P$ & mutant cells increased proliferation  \\
  \hline
 $K_0$ & EC50 term for negative feedback of tissue cells on own proliferation\\
 \hline
 $K_1$ & EC50 term for probability of NK cell finding mutant cell\\
 \hline
  $K_2$ & EC50 term for Treg inhibition of cytotoxic functions  \\
  \hline
  $K_3$ & EC50 term for how much TGF-$\beta$ each cell has \\
  \hline
 $E_\text{NK}$ & rate of NKs clearing mutants  \\
  \hline
  $E_\text{CTL}$ & rate of CTLs clearing mutants \\
  \hline
  $\sigma_\text{NK}$ & NK source rate \\ 
  \hline
  $\sigma_\text{CTL}$ & CTL source rate per cleared mutant cell \\ 
  \hline
  $\sigma_\text{Treg}$ & Treg source rate per cleared mutant cell \\ 
  \hline
  $k_\text{EMT}$ & EMT/MET rate  \\
  \hline
  $\sigma$ & standard deviation of noise in TGF-$\beta$ each cell receives  \\
  \hline
 $\tau_\text{max}$ & max amount of TGF-$\beta$ any cell can receive \\
  \hline 
 $\tau_\text{MUT}$ & rate of TGF-$\beta$ production by mutant cells\\
  \hline
 $\tau_\text{Treg}$ & rate of TGF-$\beta$ production by Treg\\
  \hline
\end{longtable}
\end{center}

\begin{center}
 \begin{longtable}{|| c | p{7cm} | c | c ||} 
 \hline
 Name & Description & INFL Low Value & INFL High Value  \\ [0.5ex] 
 \hline\hline
  $p$ & proliferation rate of tissue cells & 0.28 & \\ 
 \hline
 $d_C$  & death rate of tissue cells & 0.14 & \\
 \hline
$\Delta_\text{MIE}$ &  MIE & 0.6 & \\
 \hline
 $\Delta_\text{MGA}$ & MGA  & 0.2 &  \\
 \hline
  $\Delta_A$ & mutant cells decreased apoptosis & 0.3 &  \\
  \hline
  $\Delta_\text{IE}$ & mutant cells increased immune evasion & 0.48 &  \\
  \hline
  $\Delta_P$ & mutant cells increased proliferation & 0.36 &  \\
  \hline
 $K_0$ & EC50 term for negative feedback of tissue cells on own proliferation & 80 & \\
 \hline
 $K_1$ & EC50 term for probability of NK cell finding mutant cell & 8 & \\
 \hline
  $K_2$ & EC50 term for Treg inhibition of cytotoxic functions & 5 & 0.025  \\
  \hline
  $K_3$ & EC50 term for how much TGF-$\beta$ each cell has & 200 & \\
  \hline
 $E_\text{NK}$ & rate of NKs clearing mutants & 10 & 30  \\
  \hline
  $E_\text{CTL}$ & rate of CTLs clearing mutants & 200 & 600 \\
  \hline
  $\sigma_\text{NK}$ & NK source rate & 1.3 &  \\ 
  \hline
  $\sigma_\text{CTL}$ & CTL source rate per cleared mutant cell & 100 & \\ 
  \hline
  $\sigma_\text{Treg}$ & Treg source rate per cleared mutant cell & 200 & \\ 
  \hline
  $k_\text{EMT}$ & EMT/MET rate & 0.01 & \\
  \hline
  $\sigma$ & standard deviation of noise in TGF-$\beta$ each cell receives & 6 & \\
  \hline
 $\tau_\text{max}$ & max amount of TGF-$\beta$ any cell can receive & 500 &\\
  \hline 
 $\tau_\text{MUT}$ & rate of TGF-$\beta$ production by mutant cells & 0.05 & \\
  \hline
 $\tau_\text{Treg}$ & rate of TGF-$\beta$ production by Treg & 0.5 & \\
  \hline
  & RP Cancer Line  & 0.5 &  \\ 
 \hline
&  INFL High Duration & 30&   \\
 \hline
 & INFL Low Duration &30 &   \\
 \hline
& Mes Threshold & 0.7 &    \\
 \hline
  & maximum initial mutation damage after warmup  & 0.01 &\\
  \hline
  & increase in probability to mutate for non-mutating proliferating cells & 0.0001 & \\
  \hline
\end{longtable}
\end{center}

>>>>

\begin{table}[H]
\begin{center}
 \begin{tabular}{|| c | c||} 
 \hline
 Name & Description  \\ [0.5ex] 
 \hline
 $p$ & proliferation rate of tissue cells \\ 
 \hline
 $d_C$  & death rate of tissue cells \\
 \hline
$\Delta_\text{MIE}$ &  mesenchymal immune evasion \\
 \hline
 $\Delta_\text{MGA}$ & mesenchymal growth arrest    \\
 \hline
  $\Delta_A$ & mutant cells decreased apoptosis  \\
  \hline
  $\Delta_\text{IE}$ & mutant cells increased immune evasion  \\
  \hline
  $\Delta_P$ & mutant cells increased proliferation  \\
  \hline
 $K_0$ & EC50 term for negative feedback of tissue cells on own proliferation\\
 \hline
 $K_1$ & EC50 term for probability of NK cell finding mutant cell\\
 \hline
  $K_2$ & EC50 term for Treg inhibition of cytotoxic functions  \\
  \hline
  $K_3$ & EC50 term for how much TGF-$\beta$ each cell has \\
  \hline
 $E_\text{NK}$ & rate of NKs clearing mutants  \\
  \hline
  $E_\text{CTL}$ & rate of CTLs clearing mutants \\
  \hline
  $\sigma_\text{NK}$ & NK source rate \\ 
  \hline
  $\sigma_\text{CTL}$ & CTL source rate per cleared mutant cell \\ 
  \hline
  $\sigma_\text{Treg}$ & Treg source rate per cleared mutant cell \\ 
  \hline
  $k_\text{EMT}$ & EMT/MET rate  \\
  \hline
  $\sigma$ & standard deviation of noise in TGF-$\beta$ each cell receives  \\
  \hline
 $\tau_\text{max}$ & max amount of TGF-$\beta$ any cell can receive \\
  \hline 
 $\tau_\text{MUT}$ & rate of TGF-$\beta$ production by mutant cells\\
  \hline
 $\tau_\text{Treg}$ & rate of TGF-$\beta$ production by Treg\\
  \hline
\end{tabular}
  \caption{The model parameter names and descriptions. Note that many of these values are affected by the inflammation state of the system.}
\end{center}
\end{table}

\begin{table}[H]
\begin{center}
 \begin{tabular}{|| c | p{7cm} | c | c ||} 
 \hline
 Name & Description & INFL Low Value & INFL High Value  \\ [0.5ex] 
 \hline\hline
  $p$ & proliferation rate of tissue cells & 0.28 & \\ 
 \hline
 $d_C$  & death rate of tissue cells & 0.14 & \\
 \hline
$\Delta_\text{MIE}$ &  MIE & 0.6 & \\
 \hline
 $\Delta_\text{MGA}$ & MGA  & 0.2 &  \\
 \hline
  $\Delta_A$ & mutant cells decreased apoptosis & 0.3 &  \\
  \hline
  $\Delta_\text{IE}$ & mutant cells increased immune evasion & 0.48 &  \\
  \hline
  $\Delta_P$ & mutant cells increased proliferation & 0.36 &  \\
  \hline
 $K_0$ & EC50 term for negative feedback of tissue cells on own proliferation & 80 & \\
 \hline
 $K_1$ & EC50 term for probability of NK cell finding mutant cell & 8 & \\
 \hline
  $K_2$ & EC50 term for Treg inhibition of cytotoxic functions & 5 & 0.025  \\
  \hline
  $K_3$ & EC50 term for how much TGF-$\beta$ each cell has & 200 & \\
  \hline
 $E_\text{NK}$ & rate of NKs clearing mutants & 10 & 30  \\
  \hline
  $E_\text{CTL}$ & rate of CTLs clearing mutants & 200 & 600 \\
  \hline
  $\sigma_\text{NK}$ & NK source rate & 1.3 &  \\ 
  \hline
  $\sigma_\text{CTL}$ & CTL source rate per cleared mutant cell & 100 & \\ 
  \hline
  $\sigma_\text{Treg}$ & Treg source rate per cleared mutant cell & 200 & \\ 
  \hline
  $k_\text{EMT}$ & EMT/MET rate & 0.01 & \\
  \hline
  $\sigma$ & standard deviation of noise in TGF-$\beta$ each cell receives & 6 & \\
  \hline
 $\tau_\text{max}$ & max amount of TGF-$\beta$ any cell can receive & 500 &\\
  \hline 
 $\tau_\text{MUT}$ & rate of TGF-$\beta$ production by mutant cells & 0.05 & \\
  \hline
 $\tau_\text{Treg}$ & rate of TGF-$\beta$ production by Treg & 0.5 & \\
  \hline
  & RP Cancer Line  & 0.5 &  \\ 
 \hline
&  INFL High Duration & 30&   \\
 \hline
 & INFL Low Duration &30 &   \\
 \hline
& Mes Threshold & 0.7 &    \\
 \hline
  & maximum initial mutation damage after warmup  & 0.01 &\\
  \hline
  & increase in probability to mutate for non-mutating proliferating cells & 0.0001 & \\
  \hline
\end{tabular}
  \caption{The model parameter names, descriptions, and values during both low and high inflammation. Parameters with only one value do not change with the inflammatory state.}
\end{center}
\end{table}
